Age-related changes in plant growth and traits

### 2015-05-20 results_best.Rmd
Rename downstream variables

yvar2 <- "RA"
xvar2 <- "FinalWeight"

@@

plot(ReproInv~FinalWeight, SummaryInd, log="xy",col=col.spp[as.factor(species)],pch=16)
legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")

@@

```{r, echo=FALSE,message=FALSE}
mod <- lm (log(FinalWeight)~log(ReproInv), data=subset(SummaryInd,ReproInv>0))
plot(ReproInv~FinalWeight,data=subset(SummaryInd,ReproInv>0), log="xy",col=col.spp[as.factor(species)], pch=16)
legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
words.bottom.right.logxy(mod)

mod <- lm (log(FinalWeight)~log(Prop), data=subset(SummaryInd,Prop>0))
plot(Prop~FinalWeight,data=subset(SummaryInd,Prop>0), log="xy",col=col.spp[as.factor(species)], pch=16)
legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
words.bottom.right.logxy(mod)

mod <- lm (log(FinalWeight)~log(Prop+PD), data=subset(SummaryInd,Prop>0))
plot((Prop+PD)~FinalWeight,data=subset(SummaryInd,Prop>0), log="xy",col=col.spp[as.factor(species)], pch=16)
legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
words.bottom.right.logxy(mod)

mod <- lm (log(FinalWeight)~log(PrePol_All), data=subset(SummaryInd,PrePol_All>0))
plot((PrePol_All)~FinalWeight,data=subset(SummaryInd,PrePol_All>0), log="xy",col=col.spp[as.factor(species)], pch=16)
legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
words.bottom.right.logxy(mod)
```

@@

##Across species patterns of note
###Size versus proportional propagule investment
- Species that are bigger (by weight) invest a lower proportion of their reproduction in propagules  
   1.  This is another way of showing that larger species get less of a return on their investment in reproduction. They have higher accessory costs. 
   - There is also an increase in propagule investment with age
```{r, echo=FALSE,message=FALSE, fig.width=14, fig.height=7, out.width=792, out.height=576}
mod <- lm(log(FinalWeight) ~ (log(PerPropagule))+age,data=subset(SummaryInd,PerPropagule>0))
summary(mod)
plot(PerPropagule ~FinalWeight, data=subset(SummaryInd,RA>0&PerPropagule>0),log="xy", col=col.spp[as.factor(species)],pch=16)
legend("bottomleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
words.top.right.logxy(mod)
text(10^((0.70*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),10^((0.85*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),"includes age effect",adj=0) 
```

- Species that are bigger also invest a lower proportion of their TOTAL surplus energy in propagules (proportion propagules*RA) 
  + This is noisier than looking simply at proportion reproductive allocation to propagules, because of the RA effects - see below
```{r, echo=FALSE, message=FALSE}
mod <- lm(log(FinalWeight) ~ (log(PropAllocation))*age,data=subset(SummaryInd,PerPropagule>0))
plot(PropAllocation ~FinalWeight, data=subset(SummaryInd,RA>0&PerPropagule>0),log="xy", col=col.spp[as.factor(species)],pch=16)
legend("bottomleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
words.top.right.logxy(mod)
text(1000,.6e-4,"includes age effect (increase in Prop Allocation with age)",adj=0)
summary(mod)
```

- Looking at RA with plant size is not very informative, because:
  1. RA increases with plant size within a species  
  2. decreases with plant size across species  
  3. in combination they are noisy
- The first plot is all points  
- The second plot is just 7-year olds, showing the decrease in RA with plant size  
```{r, echo=FALSE, message=FALSE}
mod <- lm(log(FinalWeight) ~ (log(RA)),data=subset(SummaryInd,RA>0))
plot(RA ~FinalWeight, data=subset(SummaryInd,RA>0),log="xy", col=col.spp[as.factor(species)],pch=16)
legend("bottomleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
words.bottom.right.logxy(mod)
anova(mod)

mod <- lm(log(FinalWeight) ~ (log(RA)),data=subset(SummaryInd,RA>5e-3&age==7))
plot(RA ~FinalWeight, data=subset(SummaryInd,RA>5e-3&age==7),log="xy", col=col.spp[as.factor(species)],pch=16)
legend("bottomleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
words.top.right.logxy(mod)
```

- A model including the effect of both PerPropagule and RA on FinalWeight confirms this - there is a strong species effect and strong PerPropagule effect, but RA is much less significant  
```{r, echo=FALSE, message=FALSE}
mod <- lm(log(FinalWeight) ~ (log(RA))*log(PerPropagule)*species,data=subset(SummaryInd,PerPropagule>0))
anova(mod)
```

- Proportional investment in all pre-pollination tissues is uncorrelated with plant size (at most ages)  
  +  if age included in model, becomes highly significant  
```{r, echo=FALSE, message=FALSE}
mod <- lm(log(FinalWeight) ~ asin(sqrt(PerPrePol_All)),data=subset(SummaryInd,PerPrePol_All>0&age>3))
plot(asin(sqrt(PerPrePol_All)) ~ FinalWeight, data=subset(SummaryInd,PerPrePol_All>0),log="x", col=col.spp[as.factor(species)],pch=16)
legend("bottomleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
words.top.right.logx(mod)
```

- Shifts in packaging and dispersal costs with plant weight
- Species very different from one another, but no shift with size 
- Also no pattern w/r RA (not shown)
```{r, echo=FALSE, message=FALSE}
mod <- lm(log(FinalWeight) ~ asin(sqrt(PerPackDisp)),data=subset(SummaryInd,PerPackDisp>0))
plot(asin(sqrt(PerPackDisp)) ~FinalWeight, data=subset(SummaryInd,PerPackDisp>0),log="x", col=col.spp[as.factor(species)],pch=16)
legend("bottomleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
words.top.right.logx(mod)
```

@@

##Within species (across age, size, or RA) patterns to note
- Only COER and HATE increase allocation to propagules with increased plant size  
- This, together with other plots, indicates that only the plants (of a species) that have higher RA, have higher propagule investment; but not all bigger individuals have higher RA
NOTE: Plot nearly same as above, except y-axis arcsine transformed, not log transformed and R^2 values without species term
```{r, echo=FALSE, message=FALSE}
yvar <- "PerPropagule"
xvar <- "FinalWeight"

@@

mod <- lm(log(FinalWeight)~asin(sqrt(PerPropagule)),data=subset(SummaryInd,PerPropagule>0))
plot(asin(sqrt(PerPropagule))~log(FinalWeight), data=subset(SummaryInd,PerPropagule>0),col=col.spp[as.factor(species)],pch=16)
legend("bottomleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
words.top.right(mod)
```

@@

###Change in proportional allocation to pre-pollination tissues with plant weight 
- only a few species show a significant correlation -> as plants grow, they don't shift this allocation  
```{r, echo=FALSE, message=FALSE}
yvar <- "PerPrePol_All"
xvar <- "FinalWeight"

@@

```{r, echo=FALSE, message=FALSE}
par(mfrow=c(2,2), cex=1, omi=c(.1,0.1,0.1,0.1), mai=c(1.2,1,0.1,0.1))
mod <- lm(log(FinalWeight)~log(seedset),data=subset(SummaryInd,seedset>0))
plot(seedset ~ FinalWeight,data=subset(SummaryInd,seedset>0),
          col=col.spp[as.factor(species)],
          pch=16,log="xy",xlab="",ylab="seed set")
words.bottom.right.logxy(mod)

mod <- lm(log(RA)~log(seedset),data=subset(SummaryInd,seedset>0))
plot(seedset ~ RA,data=subset(SummaryInd,seedset>0),
          col=col.spp[as.factor(species)],
          pch=16,log="xy",ylab="",xlab="")
words.bottom.right.logxy(mod)
mod <- lm(log(FinalWeight)~log(seed_count),data=subset(SummaryInd,seed_count>0))
plot(seed_count ~ FinalWeight,data=subset(SummaryInd,seed_count>0),
          col=col.spp[as.factor(species)],
          pch=16,log="xy",xlab="plant weight",ylab="seed count")
words.bottom.right.logxy(mod)
mod <- lm(log(RA)~log(seed_count),data=subset(SummaryInd,seed_count>0))
plot(seed_count ~ RA,data=subset(SummaryInd,seed_count>0),
          col=col.spp[as.factor(species)],
          pch=16,log="xy",ylab="")
words.bottom.right.logxy(mod)
legend("bottomleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
```

```{r, echo=FALSE, message=FALSE}
mod <- lm(log(FinalWeight)~log(PerPropagule),data=subset(SummaryInd,seedset>0))
plot(PerPropagule~FinalWeight,data=subset(SummaryInd,PerPropagule>0),col=col.spp[as.factor(species)],pch=16,log="xy")
legend("bottomleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
words.top.right.logxy(mod)
```

- However, as shown above, there is no clear shift across plant size in pre-pollination allocation   
```{r, echo=FALSE, message=FALSE}
mod <- lm(asin(sqrt(PerPrePol_All)) ~log(FinalWeight)*age, data=subset(SummaryInd,PerPrePol_All>0))
anova(mod)
```

- There is however a decrease in RA with plant size at a given age (across species effect)
```{r, echo=FALSE, message=FALSE}
mod <- lm(asin(sqrt(RA)) ~ log(FinalWeight)*age, data=subset(SummaryInd,RA>0))
plot(asin(sqrt(RA))~FinalWeight,data=subset(SummaryInd,seedset>0),col=col.spp[as.factor(species)],pch=16,log="x")
legend("bottomleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
words.top.right.logx(mod)
anova(mod)
```

@@

- there is no relationship between seed_count and Final Weight
```{r, echo=FALSE, message=FALSE}
mod <- lm(log(FinalWeight)~log(seed_count),data=subset(SummaryInd,seed_count>0))
plot(seed_count~FinalWeight,data=subset(SummaryInd,seed_count>0),col=col.spp[as.factor(species)],pch=16,log="xy")
legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
words.bottom.right.logxy(mod)
```

```{r, echo=FALSE, message=FALSE}
mod <- lm(log(FinalWeight)~log(fruit_weight),data=subset(SummaryInd,fruit_weight>0))
plot(fruit_weight~FinalWeight,data=subset(SummaryInd,fruit_weight>0),col=col.spp[as.factor(species)],pch=16,log="xy")
legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
words.bottom.right.logxy(mod)
```

>>>>

yvar2 <- "RA"
xvar2 <- "total_weight"

@@

plot(ReproInv~total_weight, SummaryInd, log="xy",col=col.spp[as.factor(species)],pch=16)
legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")

@@

```{r, echo=FALSE,message=FALSE}
mod <- lm (log(total_weight)~log(ReproInv), data=subset(SummaryInd,ReproInv>0))
plot(ReproInv~total_weight,data=subset(SummaryInd,ReproInv>0), log="xy",col=col.spp[as.factor(species)], pch=16)
legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
words.bottom.right.logxy(mod)

mod <- lm (log(total_weight)~log(Prop), data=subset(SummaryInd,Prop>0))
plot(Prop~total_weight,data=subset(SummaryInd,Prop>0), log="xy",col=col.spp[as.factor(species)], pch=16)
legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
words.bottom.right.logxy(mod)

mod <- lm (log(total_weight)~log(Prop+PD), data=subset(SummaryInd,Prop>0))
plot((Prop+PD)~total_weight,data=subset(SummaryInd,Prop>0), log="xy",col=col.spp[as.factor(species)], pch=16)
legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
words.bottom.right.logxy(mod)

mod <- lm (log(total_weight)~log(PrePol_All), data=subset(SummaryInd,PrePol_All>0))
plot((PrePol_All)~total_weight,data=subset(SummaryInd,PrePol_All>0), log="xy",col=col.spp[as.factor(species)], pch=16)
legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
words.bottom.right.logxy(mod)
```

@@

##Across species patterns of note
###Size versus proportional propagule investment
- Species that are bigger (by weight) invest a lower proportion of their reproduction in propagules  
   1.  This is another way of showing that larger species get less of a return on their investment in reproduction. They have higher accessory costs. 
   - There is also an increase in propagule investment with age
```{r, echo=FALSE,message=FALSE, fig.width=14, fig.height=7, out.width=792, out.height=576}
mod <- lm(log(total_weight) ~ (log(PerPropagule))+age,data=subset(SummaryInd,PerPropagule>0))
summary(mod)
plot(PerPropagule ~total_weight, data=subset(SummaryInd,RA>0&PerPropagule>0),log="xy", col=col.spp[as.factor(species)],pch=16)
legend("bottomleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
words.top.right.logxy(mod)
text(10^((0.70*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),10^((0.85*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),"includes age effect",adj=0) 
```

- Species that are bigger also invest a lower proportion of their TOTAL surplus energy in propagules (proportion propagules*RA) 
  + This is noisier than looking simply at proportion reproductive allocation to propagules, because of the RA effects - see below
```{r, echo=FALSE, message=FALSE}
mod <- lm(log(total_weight) ~ (log(PropAllocation))*age,data=subset(SummaryInd,PerPropagule>0))
plot(PropAllocation ~total_weight, data=subset(SummaryInd,RA>0&PerPropagule>0),log="xy", col=col.spp[as.factor(species)],pch=16)
legend("bottomleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
words.top.right.logxy(mod)
text(1000,.6e-4,"includes age effect (increase in Prop Allocation with age)",adj=0)
summary(mod)
```

- Looking at RA with plant size is not very informative, because:
  1. RA increases with plant size within a species  
  2. decreases with plant size across species  
  3. in combination they are noisy
- The first plot is all points  
- The second plot is just 7-year olds, showing the decrease in RA with plant size  
```{r, echo=FALSE, message=FALSE}
mod <- lm(log(total_weight) ~ (log(RA)),data=subset(SummaryInd,RA>0))
plot(RA ~total_weight, data=subset(SummaryInd,RA>0),log="xy", col=col.spp[as.factor(species)],pch=16)
legend("bottomleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
words.bottom.right.logxy(mod)
anova(mod)

mod <- lm(log(total_weight) ~ (log(RA)),data=subset(SummaryInd,RA>5e-3&age==7))
plot(RA ~total_weight, data=subset(SummaryInd,RA>5e-3&age==7),log="xy", col=col.spp[as.factor(species)],pch=16)
legend("bottomleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
words.top.right.logxy(mod)
```

- A model including the effect of both PerPropagule and RA on total_weight confirms this - there is a strong species effect and strong PerPropagule effect, but RA is much less significant  
```{r, echo=FALSE, message=FALSE}
mod <- lm(log(total_weight) ~ (log(RA))*log(PerPropagule)*species,data=subset(SummaryInd,PerPropagule>0))
anova(mod)
```

- Proportional investment in all pre-pollination tissues is uncorrelated with plant size (at most ages)  
  +  if age included in model, becomes highly significant  
```{r, echo=FALSE, message=FALSE}
mod <- lm(log(total_weight) ~ asin(sqrt(PerPrePol_All)),data=subset(SummaryInd,PerPrePol_All>0&age>3))
plot(asin(sqrt(PerPrePol_All)) ~ total_weight, data=subset(SummaryInd,PerPrePol_All>0),log="x", col=col.spp[as.factor(species)],pch=16)
legend("bottomleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
words.top.right.logx(mod)
```

- Shifts in packaging and dispersal costs with plant weight
- Species very different from one another, but no shift with size 
- Also no pattern w/r RA (not shown)
```{r, echo=FALSE, message=FALSE}
mod <- lm(log(total_weight) ~ asin(sqrt(PerPackDisp)),data=subset(SummaryInd,PerPackDisp>0))
plot(asin(sqrt(PerPackDisp)) ~total_weight, data=subset(SummaryInd,PerPackDisp>0),log="x", col=col.spp[as.factor(species)],pch=16)
legend("bottomleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
words.top.right.logx(mod)
```

@@

##Within species (across age, size, or RA) patterns to note
- Only COER and HATE increase allocation to propagules with increased plant size  
- This, together with other plots, indicates that only the plants (of a species) that have higher RA, have higher propagule investment; but not all bigger individuals have higher RA
NOTE: Plot nearly same as above, except y-axis arcsine transformed, not log transformed and R^2 values without species term
```{r, echo=FALSE, message=FALSE}
yvar <- "PerPropagule"
xvar <- "total_weight"

@@

mod <- lm(log(total_weight)~asin(sqrt(PerPropagule)),data=subset(SummaryInd,PerPropagule>0))
plot(asin(sqrt(PerPropagule))~log(total_weight), data=subset(SummaryInd,PerPropagule>0),col=col.spp[as.factor(species)],pch=16)
legend("bottomleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
words.top.right(mod)
```

@@

###Change in proportional allocation to pre-pollination tissues with plant weight 
- only a few species show a significant correlation -> as plants grow, they don't shift this allocation  
```{r, echo=FALSE, message=FALSE}
yvar <- "PerPrePol_All"
xvar <- "total_weight"

@@

```{r, echo=FALSE, message=FALSE}
par(mfrow=c(2,2), cex=1, omi=c(.1,0.1,0.1,0.1), mai=c(1.2,1,0.1,0.1))
mod <- lm(log(total_weight)~log(seedset),data=subset(SummaryInd,seedset>0))
plot(seedset ~ total_weight,data=subset(SummaryInd,seedset>0),
          col=col.spp[as.factor(species)],
          pch=16,log="xy",xlab="",ylab="seed set")
words.bottom.right.logxy(mod)

mod <- lm(log(RA)~log(seedset),data=subset(SummaryInd,seedset>0))
plot(seedset ~ RA,data=subset(SummaryInd,seedset>0),
          col=col.spp[as.factor(species)],
          pch=16,log="xy",ylab="",xlab="")
words.bottom.right.logxy(mod)
mod <- lm(log(total_weight)~log(seed_count),data=subset(SummaryInd,seed_count>0))
plot(seed_count ~ total_weight,data=subset(SummaryInd,seed_count>0),
          col=col.spp[as.factor(species)],
          pch=16,log="xy",xlab="plant weight",ylab="seed count")
words.bottom.right.logxy(mod)
mod <- lm(log(RA)~log(seed_count),data=subset(SummaryInd,seed_count>0))
plot(seed_count ~ RA,data=subset(SummaryInd,seed_count>0),
          col=col.spp[as.factor(species)],
          pch=16,log="xy",ylab="")
words.bottom.right.logxy(mod)
legend("bottomleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
```

```{r, echo=FALSE, message=FALSE}
mod <- lm(log(total_weight)~log(PerPropagule),data=subset(SummaryInd,seedset>0))
plot(PerPropagule~total_weight,data=subset(SummaryInd,PerPropagule>0),col=col.spp[as.factor(species)],pch=16,log="xy")
legend("bottomleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
words.top.right.logxy(mod)
```

- However, as shown above, there is no clear shift across plant size in pre-pollination allocation   
```{r, echo=FALSE, message=FALSE}
mod <- lm(asin(sqrt(PerPrePol_All)) ~log(total_weight)*age, data=subset(SummaryInd,PerPrePol_All>0))
anova(mod)
```

- There is however a decrease in RA with plant size at a given age (across species effect)
```{r, echo=FALSE, message=FALSE}
mod <- lm(asin(sqrt(RA)) ~ log(total_weight)*age, data=subset(SummaryInd,RA>0))
plot(asin(sqrt(RA))~total_weight,data=subset(SummaryInd,seedset>0),col=col.spp[as.factor(species)],pch=16,log="x")
legend("bottomleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
words.top.right.logx(mod)
anova(mod)
```

@@

- there is no relationship between seed_count and Final Weight
```{r, echo=FALSE, message=FALSE}
mod <- lm(log(total_weight)~log(seed_count),data=subset(SummaryInd,seed_count>0))
plot(seed_count~total_weight,data=subset(SummaryInd,seed_count>0),col=col.spp[as.factor(species)],pch=16,log="xy")
legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
words.bottom.right.logxy(mod)
```

```{r, echo=FALSE, message=FALSE}
mod <- lm(log(total_weight)~log(fruit_weight),data=subset(SummaryInd,fruit_weight>0))
plot(fruit_weight~total_weight,data=subset(SummaryInd,fruit_weight>0),col=col.spp[as.factor(species)],pch=16,log="xy")
legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
words.bottom.right.logxy(mod)
```

### 2015-05-20 results_growth.Rmd
Rename downstream variables

```{r, echo=FALSE, message=FALSE}
plot((FinalWeight~PropH), SummaryInd, col=col.spp[as.factor(species)],pch=16,log="y")
legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")

yvar <- "FinalWeight"
xvar <- "PropH"

@@

###Growth Investment versus weight   
- showing that slope continues to be 1:1, but intercept decreases with time because more standing biomass
```{r, echo=FALSE, message=FALSE}
plot((GrowthInv~FinalWeight), SummaryInd, log="xy", col=col.spp[as.factor(species)],pch=16)
abline(0,1,lwd=2)
legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")

plot(GrowthInv~FinalWeight, SummaryInd, log="xy", col=col.age[as.factor(age)],pch=16)
abline(0,1,lwd=2)
legend("topleft",legend=names(labels.age),col=col.age,pch=16, cex=.8,bty="n")
```

@@

```{r, echo=FALSE,message=FALSE}
plot(total_leaf_weight~FinalWeight,SummaryInd, log="xy",col=col.age[as.factor(age)], pch=16, cex=0.8)
legend("bottomright",col=col.age, labels.age, pch=16, cex=1, bty="n")

plot(total_leaf_weight~FinalWeight,SummaryInd, log="xy",col=col.spp[as.factor(species)], pch=16, cex=0.8)
legend("bottomright",col=col.spp, labels.spp, pch=16, cex=.8, bty="n")
```

@@

plot((change_shoot_area/10000) ~ FinalBasalDiamAv,data=subset(SummaryInd), log="xy",col=col.spp[as.factor(species)], pch=16,ylim=c(0.01,500),cex=.7)
points((change_basal_area) ~ FinalBasalDiamAv,data=subset(SummaryInd), log="xy",col=col.spp[as.factor(species)], pch=1)

plot((change_shoot_area/10000) ~ FinalBasalDiamAv,data=subset(SummaryInd), log="xy",col=col.age[as.factor(age)], pch=16,ylim=c(0.01,500),cex=.7)
points((change_basal_area) ~ FinalBasalDiamAv,data=subset(SummaryInd), log="xy",col=col.age[as.factor(age)], pch=1)

>>>>

```{r, echo=FALSE, message=FALSE}
plot((total_weight~PropH), SummaryInd, col=col.spp[as.factor(species)],pch=16,log="y")
legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")

yvar <- "total_weight"
xvar <- "PropH"

@@

###Growth Investment versus weight   
- showing that slope continues to be 1:1, but intercept decreases with time because more standing biomass
```{r, echo=FALSE, message=FALSE}
plot((GrowthInv~total_weight), SummaryInd, log="xy", col=col.spp[as.factor(species)],pch=16)
abline(0,1,lwd=2)
legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")

plot(GrowthInv~total_weight, SummaryInd, log="xy", col=col.age[as.factor(age)],pch=16)
abline(0,1,lwd=2)
legend("topleft",legend=names(labels.age),col=col.age,pch=16, cex=.8,bty="n")
```

@@

```{r, echo=FALSE,message=FALSE}
plot(total_leaf_weight~total_weight,SummaryInd, log="xy",col=col.age[as.factor(age)], pch=16, cex=0.8)
legend("bottomright",col=col.age, labels.age, pch=16, cex=1, bty="n")

plot(total_leaf_weight~total_weight,SummaryInd, log="xy",col=col.spp[as.factor(species)], pch=16, cex=0.8)
legend("bottomright",col=col.spp, labels.spp, pch=16, cex=.8, bty="n")
```

@@

plot((change_shoot_area/10000) ~ dia,data=subset(SummaryInd), log="xy",col=col.spp[as.factor(species)], pch=16,ylim=c(0.01,500),cex=.7)
points((change_basal_area) ~ dia,data=subset(SummaryInd), log="xy",col=col.spp[as.factor(species)], pch=1)

plot((change_shoot_area/10000) ~ dia,data=subset(SummaryInd), log="xy",col=col.age[as.factor(age)], pch=16,ylim=c(0.01,500),cex=.7)
points((change_basal_area) ~ dia,data=subset(SummaryInd), log="xy",col=col.age[as.factor(age)], pch=1)

### 2015-05-20 results_leaf_lifespan.rmd
Rename downstream variables

If leaf lifespan based on leaf births is used instead, there are a number of significant INCREASES in leaf lifespan with increasing size
```{r, echo=FALSE,message=FALSE}
yvar <- "LL_death"
xvar <- "FinalWeight"
data <- filter(SummaryInd,LL_death<8&age>2)

@@

The interactions terms weren't significant and were removed from the model
```{r, echo=FALSE,message=FALSE}
mod <- lm(LMA_mean~species+log(FinalWeight_mean), SummarySppAge)
summary(mod)
anova(mod)

mod <- lm(LMA_mean~species+log(FinalWeight_mean), data=subset(SummarySppAge,age>2))
summary(mod)
anova(mod)

plot(LMA_mean ~FinalWeight_mean, SummarySppAge, log="xy", col=col.spp[as.factor(species)], pch=16)
legend("topleft",col=col.spp, pch=16,legend=labels.spp,cex=.8,bty="n")

plot(LMA_mean ~FinalWeight_mean, data=subset(SummarySppAge), log="xy", col=col.age[as.factor(age)], pch=16, cex=1)
legend("topleft",col=col.age, pch=16,legend=labels.age,cex=.8,bty="n")

>>>>

If leaf lifespan based on leaf births is used instead, there are a number of significant INCREASES in leaf lifespan with increasing size
```{r, echo=FALSE,message=FALSE}
yvar <- "LL_death"
xvar <- "total_weight"
data <- filter(SummaryInd,LL_death<8&age>2)

@@

The interactions terms weren't significant and were removed from the model
```{r, echo=FALSE,message=FALSE}
mod <- lm(LMA_mean~species+log(total_weight_mean), SummarySppAge)
summary(mod)
anova(mod)

mod <- lm(LMA_mean~species+log(total_weight_mean), data=subset(SummarySppAge,age>2))
summary(mod)
anova(mod)

plot(LMA_mean ~total_weight_mean, SummarySppAge, log="xy", col=col.spp[as.factor(species)], pch=16)
legend("topleft",col=col.spp, pch=16,legend=labels.spp,cex=.8,bty="n")

plot(LMA_mean ~total_weight_mean, data=subset(SummarySppAge), log="xy", col=col.age[as.factor(age)], pch=16, cex=1)
legend("topleft",col=col.age, pch=16,legend=labels.age,cex=.8,bty="n")
